---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# contactdata <img src="man/figures/logo.svg" align="right" alt="" width="120" />

<!-- badges: start -->
[![cran version](https://www.r-pkg.org/badges/version-ago/contactdata)](https://cran.r-project.org/package=contactdata/)
[![R build status](https://github.com/Bisaloo/contactdata/workflows/R-CMD-check/badge.svg)](https://github.com/Bisaloo/contactdata/actions)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Codecov test coverage](https://codecov.io/gh/Bisaloo/contactdata/branch/main/graph/badge.svg)](https://codecov.io/gh/Bisaloo/contactdata?branch=main)
<!-- badges: end -->

The goal of contactdata is to provide access to social contact data for 152
countries. This data comes from

> Kiesha Prem, Alex R. Cook, Mark Jit, *Projecting social contact matrices in 
152 countries using contact surveys and demographic data*, PLoS Comp. Biol.
(2017), https://doi.org/10.1371/journal.pcbi.1005697.

(please cite it in your publications, alongside this package).

contactdata offers an easier access to this data, makes it readily compatible
with [tidyverse](https://www.tidyverse.org/) packages, such as 
[ggplot2](https://ggplot2.tidyverse.org/), via the `contact_countries()` 
function, and provides an easy way to harmonise country nomenclature by using
the [countrycode](https://cran.r-project.org/package=countrycode) package as
authoritative name source.

## Installation

You can install this package from CRAN:

```{r, eval = FALSE}
install.packages("contactdata")
```

or the development version from [GitHub](https://github.com/bisaloo), via my 
[r-universe](https://bisaloo.r-universe.dev/):

```{r, eval = FALSE}
install.packages("contactdata", repos = "https://bisaloo.r-universe.dev")
```

## Example

The most basic function allows you to get matrix data for a specific country:

```{r example}
library(contactdata)
contact_matrix("France")
```

You can also get several countries at once with the `contact_df_countries()`
function, as detailed in the 
[vignette](https://bisaloo.github.io/contactdata/articles/visualise.html).
