---
title: "Visualise contact matrices"
author: "Hugo Gruson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Visualise contact matrices}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 10,
  fig.width = 10
)
```

```{r}
library(contactdata)
```

In this vignette, we are going to try to visualise the contact matrices for 
9 Western Europe countries. The list of these countries is:

```{r}
countries <- c("Portugal", "Spain", "Italy", "France", "Ireland", "Belgium", "Luxembourg", "Germany", "Switzerland")
```

We can get the contact data for all these countries in a single function call 
with:

```{r}
contact_data <- contact_df_countries(countries, location = "all")
```

For the visualisation itself, we use the graphical package ggplot2, which offers
a large flexibility in terms of customisation:

```{r, eval = requireNamespace("ggplot2", quietly = TRUE)}
library(ggplot2)
ggplot(contact_data, aes(x = age_from, y = age_to, fill = contact)) + 
  geom_tile() +
  facet_wrap(~ country) +
  coord_equal()
```

The default colour palette and theme are not very suitable for our data but we
can easily edit them with:

```{r, eval = requireNamespace("ggplot2", quietly = TRUE)}
ggplot(contact_data, aes(x = age_from, y = age_to, fill = contact)) + 
  geom_tile() +
  facet_wrap(~ country) +
  coord_equal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_fill_viridis_c()
```

You can also visualise the contact data at a specific `location`, e.g. at 
school:

```{r}
contact_data <- contact_df_countries(countries, location = "school")
```

```{r, eval = requireNamespace("ggplot2", quietly = TRUE)}
ggplot(contact_data, aes(x = age_from, y = age_to, fill = contact)) + 
  geom_tile() +
  facet_wrap(~ country) +
  coord_equal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_fill_viridis_c()
```
